
I would like to express my sincere gratitude to my academic supervisor, \textbf{Dr. Zoltan Istenes}, and my industrial supervisor, \textbf{Dr. Mohammed Aldibaja}, for their continued guidance, encouragement, and generosity in sharing their knowledge throughout the course of my master’s thesis. Their insights and support were instrumental in shaping the quality and direction of this work. I also extend my sincere appreciation to the \textbf{Smart Mechatronics group at Saxion University of Applied Sciences} for hosting my thesis and providing a supportive and engaging research environment.

I am deeply thankful to the professors at the \textbf{University of Girona} and \textbf{Eötvös Loránd University} for their dedicated instruction and support from the beginning of the \textbf{IFRoS program}. Their efforts have greatly contributed to my growth and understanding in the field of robotics. I also thank the \textbf{IFRoS program coordinators} for their exceptional organization and continuous assistance throughout the program.

I would like to thank all my \textbf{classmates and friends} in the IFRoS program for their companionship, teamwork, and encouragement during this enriching journey across countries and institutions.

On a personal note, I am deeply grateful to my \textbf{parents} and my two \textbf{wonderful sisters} for their unwavering love, constant motivation, and emotional support. Their belief in me has been a continuous source of strength and inspiration throughout this academic journey.

